### 2015-12-07 ada-ftrl.tex
Use small-caps for all algorithms names

\section{AdaFTRL}
\label{section:ada-ftrl}

In this section we generalize the AdaHedge
algorithm~\cite{de-Rooij-van-Erven-Grunwald-Koolen-2014} to the OLO setting,
showing that it retains its scale-free property. The analysis is very general
and based on general properties of strongly convex functions, rather than
specific properties of the entropic regularizer like in AdaHedge.

@@

\begin{theorem}[Regret Bound]
\label{theorem:ada-ftrl-regret-bound}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset. Let $D =
\sup_{x,y \in K} \|x - y\|$ be its diameter with respect to a norm $\|\cdot\|$.
Suppose that the regularizer $R:K \to \R$ is a non-negative lower
semi-continuous function that is $\lambda$-strongly convex with respect to
$\|\cdot\|$ and is bounded from above.  The regret of AdaFTRL satisfies
$$
\Regret_T(u) \le \sqrt{3} \max\left\{D, \frac{1}{\sqrt{2\lambda}} \right\} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \left(1 + R(u) \right) \; .
$$
\end{theorem}

@@

\begin{corollary}[Regret Bound]
\label{corollary:ada-ftrl-regret-bound}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset. Suppose
$f:K \to \R$ is a non-negative lower semi-continuous function that is
$1$-strongly convex with respect to $\|\cdot\|$ and is bounded from above.  The
regret of AdaFTRL with regularizer
$$
R(w) = \frac{f(w)}{16 \cdot \sup_{v \in K} f(v)}
\qquad \text{satisfies} \qquad
\Regret_T \le
5.3 \sqrt{\sup_{v \in K} f(v) \sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{corollary}

\subsection{Proof of Regret Bound for AdaFTRL}
\label{section:ada-ftrl-regret-bound}

\begin{lemma}[Initial Regret Bound]
\label{lemma:initial-regret-bound}
AdaFTRL, for any $u \in K$ and any $u \ge 0$, satisfies
$\Regret_T(u) \le \left(1 + R(u) \right) \Delta_T$.
\end{lemma}

@@

\begin{lemma}[Recurrence]
\label{lemma:gap-recurrence}
Let $D = \sup_{u, v \in K} \|u -v\|$ be the diameter of $K$.
The sequence $\{\Delta_t\}_{t=1}^\infty$ generated by AdaFTRL satisfies for any $t \ge 1$,
$$
\Delta_t \le \Delta_{t-1} + \min \left\{ D\|\ell_t\|_*, \ \frac{\|\ell_t\|_*^2}{2\lambda \Delta_{t-1}} \right\} \; .
$$
\end{lemma}

@@

\begin{lemma}[Solution of the Recurrence]
\label{lemma:recurrence-solution}
Let $D$ be the diameter of $K$. The sequence $\{\Delta_t\}_{t=0}^\infty$
generated by AdaFTRL satisfies for any $T \ge 0$,
$$
\Delta_T \le \sqrt{3} \max\left\{D, \frac{1}{\sqrt{2\lambda}} \right\} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{lemma}
%
Proof of the Lemma~\ref{lemma:recurrence-solution} is deferred to~\ref{section:ada-ftrl-proofs}.
Theorem~\ref{theorem:ada-ftrl-regret-bound} follows from
Lemmas~\ref{lemma:initial-regret-bound}~and~\ref{lemma:recurrence-solution}.

>>>>

\section{\textsc{AdaFTRL}}
\label{section:ada-ftrl}

In this section we generalize the \textsc{AdaHedge}
algorithm~\cite{de-Rooij-van-Erven-Grunwald-Koolen-2014} to the OLO setting,
showing that it retains its scale-free property. The analysis is very general
and based on general properties of strongly convex functions, rather than
specific properties of the entropic regularizer like in \textsc{AdaHedge}.

@@

\begin{theorem}[Regret Bound]
\label{theorem:ada-ftrl-regret-bound}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset. Let $D =
\sup_{x,y \in K} \|x - y\|$ be its diameter with respect to a norm $\|\cdot\|$.
Suppose that the regularizer $R:K \to \R$ is a non-negative lower
semi-continuous function that is $\lambda$-strongly convex with respect to
$\|\cdot\|$ and is bounded from above.  The regret of \textsc{AdaFTRL} satisfies
$$
\Regret_T(u) \le \sqrt{3} \max\left\{D, \frac{1}{\sqrt{2\lambda}} \right\} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \left(1 + R(u) \right) \; .
$$
\end{theorem}

@@

\begin{corollary}[Regret Bound]
\label{corollary:ada-ftrl-regret-bound}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset. Suppose
$f:K \to \R$ is a non-negative lower semi-continuous function that is
$1$-strongly convex with respect to $\|\cdot\|$ and is bounded from above.  The
regret of \textsc{AdaFTRL} with regularizer
$$
R(w) = \frac{f(w)}{16 \cdot \sup_{v \in K} f(v)}
\qquad \text{satisfies} \qquad
\Regret_T \le
5.3 \sqrt{\sup_{v \in K} f(v) \sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{corollary}

\subsection{Proof of Regret Bound for \textsc{AdaFTRL}}
\label{section:ada-ftrl-regret-bound}

\begin{lemma}[Initial Regret Bound]
\label{lemma:initial-regret-bound}
\textsc{AdaFTRL}, for any $u \in K$ and any $u \ge 0$, satisfies
$\Regret_T(u) \le \left(1 + R(u) \right) \Delta_T$.
\end{lemma}

@@

\begin{lemma}[Recurrence]
\label{lemma:gap-recurrence}
Let $D = \sup_{u, v \in K} \|u -v\|$ be the diameter of $K$.
The sequence $\{\Delta_t\}_{t=1}^\infty$ generated by \textsc{AdaFTRL} satisfies for any $t \ge 1$,
$$
\Delta_t \le \Delta_{t-1} + \min \left\{ D\|\ell_t\|_*, \ \frac{\|\ell_t\|_*^2}{2\lambda \Delta_{t-1}} \right\} \; .
$$
\end{lemma}

@@

\begin{lemma}[Solution of the Recurrence]
\label{lemma:recurrence-solution}
Let $D$ be the diameter of $K$. The sequence $\{\Delta_t\}_{t=0}^\infty$
generated by \textsc{AdaFTRL} satisfies for any $T \ge 0$,
$$
\Delta_T \le \sqrt{3} \max\left\{D, \frac{1}{\sqrt{2\lambda}} \right\} \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{lemma}
%
Proof of the Lemma~\ref{lemma:recurrence-solution} is deferred to~\ref{section:ada-ftrl-proofs}.
Theorem~\ref{theorem:ada-ftrl-regret-bound} follows from
Lemmas~\ref{lemma:initial-regret-bound}~and~\ref{lemma:recurrence-solution}.

### 2015-12-07 introduction.tex
Add references to Mirror Descent section
Use small-caps for all algorithms names

For this reason, most of the existing OLO algorithms receive as an input---or
explicitly assume---an upper bound $B$ on the norm of the loss vectors.  The
input $B$ is often disguised as the learning rate, the regularization
parameter, or the parameter of strong convexity of the regularizer. Examples of
such algorithms include the Hedge algorithm or online projected gradient
descent with fixed learning rate.  However, these algorithms have two obvious
drawbacks.

@@

\begin{table}[t]
\fontsize{8}{8.2}\selectfont
\centering
\begin{tabular}{|p{3.6cm}|c|p{3.4cm}|c|}
\hline
\textbf{Algorithm} & \textbf{Decisions Set(s)} & \textbf{Regularizer(s)} & \textbf{Scale-Free} \\ \hline \hline
\textsc{Hedge} \cite{Freund-Schapire-1997} & Probability Simplex & Negative Entropy & No \\ \hline
\textsc{GIGA} \cite{Zinkevich-2003} & Any Bounded & $\frac{1}{2}\|w\|_2^2$ & No \\ \hline
\textsc{RDA} \cite{Xiao-2010} & \textbf{Any} & \textbf{Any Strongly Convex} & No \\ \hline
\textsc{FTRL-Proximal} \cite{McMahan-Streeter-2010,McMahan-2014} & Any Bounded & $\frac{1}{2}\|w\|_2^2 + $ any convex func. & \textbf{Yes} \\ \hline
\textsc{AdaGrad MD} \cite{Duchi-Hazan-Singer-2011} & Any Bounded & $\frac{1}{2}\|w\|_2^2 + $ any convex func. & \textbf{Yes} \\ \hline
\textsc{AdaGrad FTRL} \cite{Duchi-Hazan-Singer-2011} & \textbf{Any} & $\frac{1}{2}\|w\|_2^2 + $ any convex func. & No \\ \hline
\textsc{AdaHedge} \cite{de-Rooij-van-Erven-Grunwald-Koolen-2014} & Probability Simplex & Negative Entropy & \textbf{Yes} \\ \hline
\textsc{Optimistic MD} \cite{Rakhlin-Sridharan-2013} & $\sup_{u,v \in K} \Breg_f(u,v) < \infty$ & \textbf{Any Strongly Convex} & \textbf{Yes} \\ \hline
\textsc{NAG} \cite{Ross-Mineiro-Langford-2013} & $\{u: \max_t \langle \ell_t, u\rangle \leq C\}$ & $\frac{1}{2}\|w\|_2^2 $& Partially\footnotemark \\ \hline
\textsc{Scale invariant algorithms} \cite{Orabona-Crammer-Cesa-Bianchi-2014} & \textbf{Any} & $\frac{1}{2}\|w\|_p^2 + $ any convex func. \newline $1<p\leq2$ & Partially\textsuperscript{\ref{footnote-label}} \\ \hline
\textsc{AdaFTRL} \textbf{[this paper]} & Any Bounded & \textbf{Any Strongly Convex} & \textbf{Yes} \\ \hline
\textsc{SOLO FTRL} \textbf{[this paper]} & \textbf{Any} & \textbf{Any Strongly Convex} & \textbf{Yes} \\ \hline
\end{tabular}
\caption{Selected results for OLO. Best results in each column are in bold.
\label{table:results}
}
\end{table}

@@

A summary of algorithms for OLO is presented in Table~\ref{table:results}.
While the scale-free property has been looked at in the expert setting, in the
general OLO setting this issue has been largely ignored.  In particular, the
AdaHedge~\cite{de-Rooij-van-Erven-Grunwald-Koolen-2014} algorithm, for
prediction with expert advice, is specifically designed to be scale-free.  A
notable exception in the OLO literature is the discussion of the ``off-by-one''
issue in~\cite{McMahan-2014}, where it is explained that even the popular AdaGrad
algorithm~\cite{Duchi-Hazan-Singer-2011} is not completely adaptive; see also
our discussion in Section~\ref{section:solo-ftrl}. In particular, existing
scale-free algorithms cover only some norms/regularizers and \emph{only}
bounded decision sets. The case of \textbf{unbounded decision sets},
practically the most interesting one for machine learning applications, remains
completely unsolved.

@@

The contribution of this paper is twofold. First, in
Section~\ref{section:ada-ftrl} we show that the analysis and design of
AdaHedge can be generalized to the OLO scenario and to any strongly convex
regularizer, in an algorithm we call \textsc{AdaFTRL}, providing a new and
rather interesting way to adapt the learning rates to have scale-free
algorithms.  Second, in Section~\ref{section:solo-ftrl} we propose a new and
simple algorithm, \textsc{SOLO FTRL}, that is scale-free and is the
\textbf{first} scale-free online algorithm for unbounded sets with a
non-vacuous regret bound.  Both algorithms are instances of Follow The
Regularized Leader (FTRL) with an adaptive learning rate.  Moreover, our
algorithms show that scale-free algorithms can be obtained in a ``native'' and
simple way, i.e.  without using ``doubling tricks'' that attempt to fix poorly
designed algorithms rather than directly solving the problem.

>>>>

For this reason, most of the existing OLO algorithms receive as an input---or
explicitly assume---an upper bound $B$ on the norm of the loss vectors.  The
input $B$ is often disguised as the learning rate, the regularization
parameter, or the parameter of strong convexity of the regularizer. Examples of
such algorithms include the \textsc{Hedge} algorithm or online projected gradient
descent with fixed learning rate.  However, these algorithms have two obvious
drawbacks.

@@

\begin{table}[t]
\fontsize{8}{8.2}\selectfont
\centering
\begin{tabular}{|p{3.6cm}|c|p{3.4cm}|c|}
\hline
\textbf{Algorithm} & \textbf{Decisions Set(s)} & \textbf{Regularizer(s)} & \textbf{Scale-Free} \\ \hline \hline
\textsc{Hedge} \cite{Freund-Schapire-1997} & Probability Simplex & Negative Entropy & No \\ \hline
\textsc{GIGA} \cite{Zinkevich-2003} & Any Bounded & $\frac{1}{2}\|w\|_2^2$ & No \\ \hline
\textsc{RDA} \cite{Xiao-2010} & \textbf{Any} & \textbf{Any Strongly Convex} & No \\ \hline
\textsc{FTRL-Proximal} \cite{McMahan-Streeter-2010,McMahan-2014} & Any Bounded & $\frac{1}{2}\|w\|_2^2 + $ any convex func. & \textbf{Yes} \\ \hline
\textsc{AdaGrad MD} \cite{Duchi-Hazan-Singer-2011} & Any Bounded & $\frac{1}{2}\|w\|_2^2 + $ any convex func. & \textbf{Yes} \\ \hline
\textsc{AdaGrad FTRL} \cite{Duchi-Hazan-Singer-2011} & \textbf{Any} & $\frac{1}{2}\|w\|_2^2 + $ any convex func. & No \\ \hline
\textsc{AdaHedge} \cite{de-Rooij-van-Erven-Grunwald-Koolen-2014} & Probability Simplex & Negative Entropy & \textbf{Yes} \\ \hline
\textsc{Optimistic MD} \cite{Rakhlin-Sridharan-2013} & $\sup_{u,v \in K} \Breg_f(u,v) < \infty$ & \textbf{Any Strongly Convex} & \textbf{Yes} \\ \hline
\textsc{NAG} \cite{Ross-Mineiro-Langford-2013} & $\{u: \max_t \langle \ell_t, u\rangle \leq C\}$ & $\frac{1}{2}\|w\|_2^2 $& Partially\footnotemark \\ \hline
\textsc{Scale invariant algorithms} \cite{Orabona-Crammer-Cesa-Bianchi-2014} & \textbf{Any} & $\frac{1}{2}\|w\|_p^2 + $ any convex func. \newline $1 < p \le 2$ & Partially\textsuperscript{\ref{footnote-label}} \\ \hline
\textsc{AdaFTRL} \textbf{[this paper]} & Any Bounded & \textbf{Any Strongly Convex} & \textbf{Yes} \\ \hline
\textsc{SOLO FTRL} \textbf{[this paper]} & \textbf{Any} & \textbf{Any Strongly Convex} & \textbf{Yes} \\ \hline
\end{tabular}
\caption{Selected results for OLO. Best results in each column are in bold.
\label{table:results}
}
\end{table}

@@

A summary of algorithms for OLO is presented in Table~\ref{table:results}.
While the scale-free property has been looked at in the expert setting, in the
general OLO setting this issue has been largely ignored.  In particular, the
\textsc{AdaHedge}~\cite{de-Rooij-van-Erven-Grunwald-Koolen-2014} algorithm, for
prediction with expert advice, is specifically designed to be scale-free.  A
notable exception in the OLO literature is the discussion of the ``off-by-one''
issue in~\cite{McMahan-2014}, where it is explained that even the popular \textsc{AdaGrad}
algorithm~\cite{Duchi-Hazan-Singer-2011} is not completely adaptive; see also
our discussion in Section~\ref{section:solo-ftrl}. In particular, existing
scale-free algorithms cover only some norms/regularizers and \emph{only}
bounded decision sets. The case of \textbf{unbounded decision sets},
practically the most interesting one for machine learning applications, remains
completely unsolved.

@@

The contribution of this paper is twofold. First, in
Section~\ref{section:ada-ftrl} we show that the analysis and design of
\textsc{AdaHedge} can be generalized to the OLO scenario and to any strongly convex
regularizer, in an algorithm we call \textsc{AdaFTRL}, providing a new and
rather interesting way to adapt the learning rates to have scale-free
algorithms.  Second, in Section~\ref{section:solo-ftrl} we propose a new and
simple algorithm, \textsc{SOLO FTRL}, that is scale-free and is the
\textbf{first} scale-free online algorithm for unbounded sets with a
non-vacuous regret bound.  Both algorithms are instances of \textsc{Follow The
Regularized Leader} (\textsc{FTRL}) with an adaptive learning rate.  Moreover, our
algorithms show that scale-free algorithms can be obtained in a ``native'' and
simple way, i.e.  without using ``doubling tricks'' that attempt to fix poorly
designed algorithms rather than directly solving the problem.

### 2015-12-07 preliminaries.tex
Added explanations to Mirror Descent section.
Also, removed the extra words "Appendix" at several places.
Use small-caps for all algorithms names

The following proposition relates the range of values of a strongly convex
function to the diameter of its domain. The proof can be found in
Appendix~\ref{section:definitions-proofs}.

@@

Our scale-free online learning algorithms are versions of the \textsc{Follow
The Regularized Leader} (FTRL) algorithm with varying regularizers, presented
as Algorithm~\ref{algorithm:ftrl-varying-regularizer}.  The following lemma
bounds its regret.

>>>>

The following proposition relates the range of values of a strongly convex
function to the diameter of its domain. The proof can be found
in~\ref{section:definitions-proofs}.

@@

Our scale-free online learning algorithms are versions of the \textsc{Follow
The Regularized Leader} (\textsc{FTRL}) algorithm with varying regularizers,
presented as Algorithm~\ref{algorithm:ftrl-varying-regularizer}.  The following
lemma bounds its regret.

### 2015-12-07 solo-ftrl.tex
Added explanations to Mirror Descent section.
Also, removed the extra words "Appendix" at several places.
Use small-caps for all algorithms names

\section{SOLO FTRL}
\label{section:solo-ftrl}

The closest algorithm to a scale-free one in the OLO literature is the AdaGrad
algorithm~\cite{Duchi-Hazan-Singer-2011}.  It uses a regularizer on each
coordinate of the form
\begin{equation*}
R_t(w) = R(w) \left(\delta + \sqrt{\sum_{s=1}^{t-1} \|\ell_s\|_*^2} \right).
\end{equation*}
This kind of regularizer would yield a scale-free algorithm \emph{only} for
$\delta=0$.  Unfortunately, the regret bound in~\cite{Duchi-Hazan-Singer-2011}
becomes vacuous for such setting in the unbounded case. In fact, it requires
$\delta$ to be greater than $\|\ell_t\|_*$ for all time steps $t$, requiring
knowledge of the future (see Theorem~5 in~\cite{Duchi-Hazan-Singer-2011}). In
other words, despite of its name, AdaGrad is not fully adaptive to the norm of
the loss vectors. Identical considerations hold for the FTRL-Proximal in
\cite{McMahan-Streeter-2010,McMahan-2014}: the scale-free setting of the
learning rate is valid only in the bounded case.

One simple approach would be to use a doubling trick on $\delta$ in order to
estimate on the fly the maximum norm of the losses. Note that a naive strategy
would still fail because the initial value of $\delta$ should be data-dependent
in order to have a scale-free algorithm. Moreover, we would have to upper bound
the regret in all the rounds where the norm of the current loss is bigger than
the estimate. Finally, the algorithm would depend on an additional parameter,
the ``doubling'' power. Hence, even guaranteeing a regret bound\footnote{For
lack of space, we cannot include the regret bound for the doubling trick
version. It would be exactly the same as in
Theorem~\ref{theorem:regret-solo-ftrl}, following a similar analysis, but with
the additional parameter of the doubling power.}, such strategy would give the
feeling that FTRL needs to be ``fixed'' in order to obtain a scale-free
algorithm.

@@

\begin{theorem}[Regret of \textsc{SOLO FTRL}]
\label{theorem:regret-solo-ftrl}
Suppose $K \subseteq V$ is a non-empty closed convex subset.  Let $D =
\sup_{u,v \in K} \|u - v\|$ be its diameter with respect to a norm $\|\cdot\|$.
Suppose that the regularizer $R:K \to \R$ is a non-negative lower
semi-continuous function that is $\lambda$-strongly convex with respect to
$\|\cdot\|$. The regret of SOLO FTRL satisfies
\begin{align*}
\Regret_T(u)
& \le \left( R(u) + \frac{2.75}{\lambda}\right) \sqrt{\sum_{t=1}^{T} \norm{\ell_t}_*^2}
+ 3.5 \min\left\{\frac{\sqrt{T-1}}{\lambda} , D\right\} \max_{t \le T} \|\ell_t\|_*.
\end{align*}
\end{theorem}

When $K$ is bounded, we can choose the optimal multiple of the regularizer.  We
choose $R(w) = \lambda f(w)$ where $f$ is a $1$-strongly convex function and
optimize $\lambda$.  The result of the optimization is
Corollary~\ref{corollary:regret-solo-ftrl-bounded-set}; the proof is in
Appendix~\ref{section:solo-ftrl-proofs}.  It is similar to
Corollary~\ref{corollary:ada-ftrl-regret-bound} for AdaFTRL. The scaling
however is different in the two corollaries.  In
Corollary~\ref{corollary:ada-ftrl-regret-bound}, $\lambda \sim 1/(\sup_{v \in
K} f(v))$ while in Corollary~\ref{corollary:regret-solo-ftrl-bounded-set} we
have $\lambda \sim 1/\sqrt{\sup_{v \in K} f(v)}$.

\begin{corollary}[Regret Bound for Bounded Decision Sets]
\label{corollary:regret-solo-ftrl-bounded-set}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset.  Suppose
that $f:K \to \R$ is a non-negative lower semi-continuous function that is $1$-strongly
convex with respect to $\|\cdot\|$. SOLO FTRL with regularizer
$$
R(w) = \frac{f(w)\sqrt{2.75}}{\sqrt{\sup_{v \in K} f(v)}}
\quad \text{satisfies} \quad
\Regret_T \le 13.3 \sqrt{\sup_{v \in K} f(v) \sum_{t=1}^{T} \norm{\ell_t}_*^2} \; .
$$
\end{corollary}

\subsection{Proof of Regret Bound for SOLO FTRL}
\label{section:solo-ftrl-regret-bound}

>>>>

\section{\textsc{SOLO FTRL}}
\label{section:solo-ftrl}

The closest algorithm to a scale-free one in the OLO literature is the \textsc{AdaGrad}
algorithm~\cite{Duchi-Hazan-Singer-2011}.  It uses a regularizer on each
coordinate of the form
\begin{equation*}
R_t(w) = R(w) \left(\delta + \sqrt{\sum_{s=1}^{t-1} \|\ell_s\|_*^2} \right).
\end{equation*}
This kind of regularizer would yield a scale-free algorithm \emph{only} for
$\delta=0$.  Unfortunately, the regret bound in~\cite{Duchi-Hazan-Singer-2011}
becomes vacuous for such setting in the unbounded case. In fact, it requires
$\delta$ to be greater than $\|\ell_t\|_*$ for all time steps $t$, requiring
knowledge of the future (see Theorem~5 in~\cite{Duchi-Hazan-Singer-2011}). In
other words, despite of its name, \textsc{AdaGrad} is not fully adaptive to the norm of
the loss vectors. Identical considerations hold for the \textsc{FTRL-Proximal} in
\cite{McMahan-Streeter-2010,McMahan-2014}: the scale-free setting of the
learning rate is valid only in the bounded case.

One simple approach would be to use a doubling trick on $\delta$ in order to
estimate on the fly the maximum norm of the losses. Note that a naive strategy
would still fail because the initial value of $\delta$ should be data-dependent
in order to have a scale-free algorithm. Moreover, we would have to upper bound
the regret in all the rounds where the norm of the current loss is bigger than
the estimate. Finally, the algorithm would depend on an additional parameter,
the ``doubling'' power. Hence, even guaranteeing a regret bound\footnote{For
lack of space, we cannot include the regret bound for the doubling trick
version. It would be exactly the same as in
Theorem~\ref{theorem:regret-solo-ftrl}, following a similar analysis, but with
the additional parameter of the doubling power.}, such strategy would give the
feeling that \textsc{FTRL} needs to be ``fixed'' in order to obtain a scale-free
algorithm.

@@

\begin{theorem}[Regret of \textsc{SOLO FTRL}]
\label{theorem:regret-solo-ftrl}
Suppose $K \subseteq V$ is a non-empty closed convex subset.  Let $D =
\sup_{u,v \in K} \|u - v\|$ be its diameter with respect to a norm $\|\cdot\|$.
Suppose that the regularizer $R:K \to \R$ is a non-negative lower
semi-continuous function that is $\lambda$-strongly convex with respect to
$\|\cdot\|$. The regret of \textsc{SOLO FTRL} satisfies
\begin{align*}
\Regret_T(u)
& \le \left( R(u) + \frac{2.75}{\lambda}\right) \sqrt{\sum_{t=1}^{T} \norm{\ell_t}_*^2}
+ 3.5 \min\left\{\frac{\sqrt{T-1}}{\lambda} , D\right\} \max_{t \le T} \|\ell_t\|_*.
\end{align*}
\end{theorem}

When $K$ is bounded, we can choose the optimal multiple of the regularizer.  We
choose $R(w) = \lambda f(w)$ where $f$ is a $1$-strongly convex function and
optimize $\lambda$.  The result of the optimization is
Corollary~\ref{corollary:regret-solo-ftrl-bounded-set}; the proof is
in~\ref{section:solo-ftrl-proofs}.  It is similar to
Corollary~\ref{corollary:ada-ftrl-regret-bound} for \textsc{AdaFTRL}. The scaling
however is different in the two corollaries.  In
Corollary~\ref{corollary:ada-ftrl-regret-bound}, $\lambda \sim 1/(\sup_{v \in
K} f(v))$ while in Corollary~\ref{corollary:regret-solo-ftrl-bounded-set} we
have $\lambda \sim 1/\sqrt{\sup_{v \in K} f(v)}$.

\begin{corollary}[Regret Bound for Bounded Decision Sets]
\label{corollary:regret-solo-ftrl-bounded-set}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset.  Suppose
that $f:K \to \R$ is a non-negative lower semi-continuous function that is $1$-strongly
convex with respect to $\|\cdot\|$. \textsc{SOLO FTRL} with regularizer
$$
R(w) = \frac{f(w)\sqrt{2.75}}{\sqrt{\sup_{v \in K} f(v)}}
\quad \text{satisfies} \quad
\Regret_T \le 13.3 \sqrt{\sup_{v \in K} f(v) \sum_{t=1}^{T} \norm{\ell_t}_*^2} \; .
$$
\end{corollary}

\subsection{Proof of Regret Bound for \textsc{SOLO FTRL}}
\label{section:solo-ftrl-regret-bound}
